Macro Impacts

### 2016-08-03 Macro Impacts Revised.tex
Figured out why I was confused, and all is well

Now, for a ray that immediately hits the surface, its energy must be the same as when it started. This corresponds to $T = \to 0$ and $F_{m,n} = 1$

@@

This is, really, an upper bound to what $A$ can be, since $A$ really depends on $m$. When we fix $A$, we lose information about how the frequencies are distributed, and we, in some sense, assume that all the energy from the explosion is initially concentrated in the lower frequencies. This is good for an upper estimate of the energy felt by seismometers. Note, for bigger $k_0$, $E_m$ experiences a faster drop-off as $T$ gets big.

>>>>

Now, for a ray that immediately hits the surface, its energy must be the same as when it started. This corresponds to $T \to 0$ and $F_{m,n} = 1$

@@

Clearly, a seismometer will not detect all the energy from a macro impact, since it only detects a certain range of frequencies. Thus, by fixing $A$ as we have, we are insisting that the energy of the impact is concentrated at lower $k$. We are assuming that all the energy from the explosion is initially concentrated in the lower frequencies below $k_0$, and that it is distributed according to the leading order expression inside the integral of (172). This is good for an upper estimate of the energy felt by seismometers. Note, for bigger $k_0$, $E_m'$ experiences a faster drop-off as $T$ gets big. The choice of $k_0$ is then very important, since it fixes the rate of attenuation.
